\documentclass[a4paper,11pt]{article}
\usepackage{fullpage}

\usepackage[utf8]{inputenc}
\usepackage[british]{babel}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{color}
\usepackage{float}
\usepackage{listings}
\usepackage{fontenc}
\usepackage[hidelinks]{hyperref}

\usepackage{multirow}


\title{\textbf{EMBEDDED SIGNAL PROCESSING SYSTEMS (course 1TE682) \\
    Uppsala University -- Spring 2015 \\
    Report for Laboratory Experiment 3  }}

\author{
Tim Josefsson\\
\textup{Dept. of Information Technology}\\
\textup{Uppsala University}\\
\textup{Uppsala Sweden}\\
\textup{Tim.Josefsson.9673@student.uu.se}
\and
Philip Åkerfeldt\\
\textup{Dept. of Information Technology}\\
\textup{Uppsala University}\\
\textup{Uppsala Sweden}\\
\textup{Philip.Akerfeldt.4987@student.uu.se}
}


\date{\today}

\begin{document}
\maketitle
\newpage
\tableofcontents
\pagebreak

What does the system consist of?
What are the input and output signals of the system?
What is the impulse response of the system?
Does this system have only one impulse response?
Is the system time-invariant and linear?
Are the signals digital or analog?
What role does the embedded system (consisting of hardware and software) play in the whole system?
How to improve the accuracy of the distance meter?
The report needs to include

\section{Introduction}
Principles of the doppler effect speed measurement \\

\section{Observations}
 \\

\section{Measurements}
* Measurement of the sound speed in the air \\

\section{Discussion}
* Answers to and discussions about the above questions\\